---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spiderorchid

<!-- badges: start -->
<!-- badges: end -->

# Download and wrangle publication data for Monash EBS academic staff

## Overview

The `spiderorchid` R package provides tools to retrieve research publications from Google Scholar and ORCID, or from DOIs, along with CRAN package download statistics. It is tailored for academic researchers in the EBS department who wish to consolidate and analyze their research outputs, while also monitoring their contributions to CRAN.

The main functions included are:

* `fetch_scholar`: Retrieves publications from Google Scholar given IDs.
* `fetch_orchid`: Retrieves publications from ORCID given IDs.
* `fetch_doi`: Retrieves publications from CrossRef given DOIS.
* `fetch_cran`: Searches for CRAN packages by an author’s name and returns relevant package information such as the number of downloads and last update date.

The package caches results within each R session. So if you fetch the same data multiple times, it will only download it once.

## Installation

```r
# Install the packages needed
pak::pak(c("robjhyndman/pkgmeta", "numbats/spiderorchid"))
```

```{r}
library(spiderorchid)
library(dplyr)
```

## Dataset

`staff_ids.csv`

This dataset contains mappings between researchers' names and their respective ORCID and Google Scholar IDs. It is useful for linking and identifying academic profiles across different platforms.

```{r}
staff_ids
```

## Google scholar publications

```{r}
staff_ids |>
  filter(last_name %in% c("Negi", "Lydeamore")) |>
  pull(scholar_id) |>
  fetch_scholar()
```

## ORCID publications

The `fetch_orcid()` function requires authentication on ORCID. If you have not previously
authenticated, it will prompt you to do so when first run. If you just
follow the prompts, you will be authenticated, but only for downloading your
own papers. If you want to download papers from other ORCID IDs, you will
need to authenticate with a 2-legged OAuth. Follow the instructions at
<https://info.orcid.org/register-a-client-application-production-member-api/>.
To avoid having to do this in each session, store the token obtained from
`orcid_auth()` in your `.Renviron` file by running `usethis::edit_r_environ()`.
It should be of the form \code{ORCID_TOKEN=<your token>}.


```{r}
staff_ids |>
  filter(last_name %in% c("Negi", "Lydeamore")) |>
  pull(orcid_id) |>
  fetch_orcid()
```

## DOI publications

```{r}
fetch_doi(c("10.1016/j.ijforecast.2023.10.003", "10.1080/10618600.2020.1807353"))
```

## CRAN packages

This function retrieves information about CRAN packages authored by a specified individual. It returns a data frame containing the package name, number of downloads, the authors, and the last update date.

```{r}
fetch_cran(c(
  "Michael Lydeamore",
  "Di Cook",
  "Dianne Cook"
))
```
