---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spiderorchid

<!-- badges: start -->
<!-- badges: end -->

# Download and wrangle publication data for Monash EBS academic staff

## Overview

The `spiderorchid` R package offers tools to retrieve research publications from Google Scholar and ORCID, along with CRAN package download statistics. It is tailored for academic researchers in the EBS department who wish to consolidate and analyze their research outputs, while also monitoring their contributions to CRAN, including publication updates and downloads.

The main functions included are:

* `find_cran_packages`: Searches for CRAN packages by an author's first and last name and returns relevant package information such as the number of downloads and last update date.
* `get_publications`: Retrieves publications from both Google Scholar and ORCID based on provided IDs.
* `get_all_publications`: Retrieves publications from multiple authors.
* `cran_all_pubs`: Combines CRAN package data for multiple authors.

## Installation

```r
# Install the package
pak::pak("numbats/spiderorchid")
```

Authenticate for the ORCID API by following the instructions at <https://github.com/ropensci-archive/rorcid/blob/master/README-not.md#authentication>. We have found that the second option (a 2-legged OAuth) is necessary. Then store the token obtained from `orcid_auth()` in your `.Renviron` file by running `usethis::edit_r_environ()`. It should be of the form

```
ORCID_TOKEN=<your token>
```

```{r}
library(spiderorchid)
```

## Functions

## 1. `find_cran_packages`

This function retrieves information about CRAN packages authored by a specified individual. It returns a data frame containing the package name, number of downloads, the authors, and the last update date.

```{r}
find_cran_packages("Michael", "Lydeamore")
```

## 2. `get_publications`

This function retrieves research publications from Google Scholar and/or ORCID, combining the results into a single data frame. Both id arguments can be vectors of the same length.

```{r}
# Example 1: Retrieve publications from both ORCID and Google Scholar
get_publications(orcid_id = "0000-0002-2140-5352", scholar_id = "vamErfkAAAAJ")
```

```{r}
# Example 2: Retrieve publications only from Google Scholar
get_publications(scholar_id = "vamErfkAAAAJ")
```

```{r}
# Example 3: Retrieve publications only from ORCID
get_publications(orcid_id = "0000-0002-2140-5352")
```


## 3. `get_all_publications`

This function takes a data frame of authors, each with an ORCID ID and a Google Scholar ID, and returns their combined publications.

```{r}
eauthors_df <- tibble::tibble(
  orcid_id = c("0000-0002-2140-5352", "0000-0002-1825-0097", NA, "0000-0001-5109-3700"),
  scholar_id = c(NA, "vamErfkAAAAJ", "4bahYMkAAAAJ", NA)
)
get_all_publications(authors_df)
```

## 4. `cran_all_pubs

This function retrieves CRAN package download statistics for multiple authors by their first and last names.

```{r}
cran_authors <- tibble::tibble(
  first_name = c("Michael", "Rob"),
  last_name = c("Lydeamore", "Hyndman")
)

cran_all_pubs(cran_authors)
```

## Dataset

`staff_ids.csv`

This dataset contains mappings between researchers' names and their respective ORCID and Google Scholar IDs. It is useful for linking and identifying academic profiles across different platforms.

```{r}
print(staff_ids)
```


## Dependencies

This package relies on the following R packages:

- pkgsearch
- tibble
- dplyr
- stringr
- scholar
- rorcid

You can install these dependencies using install.packages()
```{r eval=FALSE}
install.packages(c("pkgsearch", "tibble", "dplyr", "stringr", "scholar", "rorcid"))
```


## License
MIT License



